### 2022-11-29 README.Rmd
replaced old plot functions with autoplot

Let's visualise the matrix to get a sense of the predictions with `plot_matrix`. First we need to transform the predictions to a matrix:

```{r plot-matrix-differents}
synthetic_contact_fairfield %>% 
  predictions_to_matrix() %>% 
  plot_matrix()
```

>>>>

Let's visualise the matrix to get a sense of the predictions with `autoplot`. First we need to transform the predictions to a matrix:

```{r plot-matrix-differents}
synthetic_contact_fairfield %>% 
  predictions_to_matrix() %>% 
  autoplot()
```
